---
title: "In-class Activity: Samplind Distributions"
author: "GROUP NUMBER: GROUP MEMBER NAMES"
format: html
embed-resources: true
html-math-method: mathml
execute: 
  warning: false
  echo: true
  error: false
---

```{r}
#| label: setup
#| include: FALSE
#| message: FALSE
library(mosaic)
library(ggformula)
library(readr)
```

## NFL Players in 2017

In general, we do not get to observe the entire population, which is why sampling is important. In this case, though, we will observe a completely known population, all NFL players in 2017. Let's start by learning about the population.

```{r}
#| label: read-data
nfl <- read_csv("nfl2017.csv", na = "NA") #this specifies the data use NA as the missing value placeholder
```

1. Since we know the population, the following values are actually __________________. (fill in the blank)

```{r}
#| label: stats
df_stats(~Weight, data = nfl)
```

```{r}
#| label: plot
gf_histogram(~Weight, data = nfl,
             xlab = "_______",
             ylab = "_______",
             title = "Population Distribution of NFL Player Weights")
```

2. Describe the distribution of the population:  

> Insert Answer



### Take a Sample

Now let's take a sample from the population, an act we would do if we could not have complete knowledge of the population (which is most of the time, just not in this situation).


```{r}
#|label: create-sample
sample30 <- sample(nfl, size = 30, replace = FALSE)
```


3. Now calculate the relevant summary statistics and plot the distribution of the data (recommend histogram, why?)


```{r}
#place code here
```



4. Describe the distribution of the sample data:  

>Insert Answer Here



### Generating a Sampling Distribution  

Let's generate the t-distribution for a sample of size 15. 

```{r}
#| label: create-sampling-plot-stats

pop_mean_nfl <- mean(~Weight, data = nfl)
sample_size <- 15

# number of simulations (repeated samples of the same size)
repeats <- 10000

# placeholder vector
t_stat_nfl <- numeric(repeats) 

for (i in 1:repeats) {
  
  rsample <- sample(nfl, size = sample_size, replace = FALSE)
  
  t_stat_nfl[i] <- (mean(~Weight, data = rsample) - pop_mean_nfl)/(sd(~Weight, data = rsample)/sqrt(sample_size)) #calculates the t-score

}

gf_dhistogram(~t_stat_nfl, 
              xlab = "t-Statistics for NFL Weight", ylab = "Density",
              title = "Sampling Distribution of t-Score") 


mean(~t_stat_nfl)
sd(~t_stat_nfl)
min(~t_stat_nfl)
max(~t_stat_nfl)

```

5. What do you notice about the sampling distribution of the t-statistic?

>Insert Answer 



6. If you increase sample size to 40 how does the sampling distribution change?

>Insert Answer




7. In this example we know the whole population. How can we approximate the population if all we have is a sample?

>Insert Answer



8. Let's write pseudocode - which is basically a text description of what the code will do.  Replace each line of code with a description of what it does. Here are some useful phrases

- Initialize variable  
- Start  
- Call function  
- Output/Print  
- End  

```{r}
pop_mean_nfl <- mean(~Weight, data = nfl)
sample_size <- 15

# number of simulations (repeated samples of the same size)
repeats <- 10000

# placeholder vector
t_stat_nfl <- numeric(repeats) 

for (i in 1:repeats) {
  
  rsample <- sample(nfl, size = sample_size, replace = FALSE)
  
  t_stat_nfl[i] <- (mean(~Weight, data = rsample) - pop_mean_nfl)/(sd(~Weight, data = rsample)/sqrt(sample_size)) #calculates the t-score

}

gf_dhistogram(~t_stat_nfl, 
              xlab = "t-Statistics for NFL Weight", ylab = "Density",
              title = "Sampling Distribution of t-Score") 


mean(~t_stat_nfl)
sd(~t_stat_nfl)
```
