---
title: "STAT 320 ICA: Regression Analysis"
author: "NAMES"
format: html
embed-resources: true
html-math-method: mathml
execute: 
  warning: false
  echo: true
  error: false
---


```{r}
#| label: setup
#| include: false

library(ggformula)
library(mosaic)
library(tidyverse)
library(quantreg)
# add other packages as needed
```



## Data Description
Here is data from a personal experiment to compare commuting time based on a randomized selection between two bicycles made of different materials.

Bike:	Type of material Carbon or Steel  
Date:	Date of the bike commute  
Distance:	Length of commute (in miles)  
Time:	Total commute time (hours:minutes:seconds)  
Minutes:	Time converted to minutes  
AvgSpeed:	Average speed during the ride (miles per hour)  
TopSpeed:	Maximum speed (miles per hour)  
Seconds:	Time converted to seconds  
Month:	Categories: 1Jan 2Feb 3Mar 4Apr 5May 6June 7July  


```{r}
#| label: read-data
library(Lock5Data)
data("BikeCommute")
```

Note - you can filter the data like so -  

```{r}
#| label: example-filter
#make sure the appropriate package is loaded
BikeCommute |> 
  filter(Bike == "Steel") -> just_steel

BikeCommute |> 
  filter(Bike == "Steel", Distance > 26.7) -> just_steel_no
```

```{r}
#| label: example-scatterplot
gf_point(Minutes ~ Distance, data = just_steel_no) |> 
  gf_lm()
```


```{r}
#| label: example-scatterplot-medianreg
gf_point(Minutes ~ Distance, data = just_steel_no) |> 
  gf_lm(color = "red") |> 
  gf_quantile(quantiles = 0.5, color = "blue")
```

## Build a model
Build and analyze a model for each bike type to see how commute time (Minutes) and distance (Distance) relate to each other. Be sure to provide all appropriate analysis and exploratory analysis.



