---
title: "STAT 320 ICA: Categorical Analysis"
author: "NAMES"
format: html
embed-resources: true
html-math-method: mathml
execute: 
  warning: false
  echo: true
  error: false
---


```{r}
#| label: setup
#| include: false

library(ggformula)
library(mosaic)
library(tidyverse)
library(quantreg)
# add other packages as needed
```



## Cereal Marketing within the Grocery Store
In general, companies spend a lot of time and research determining optimal location of items within a store to increase purchases. We want to see if the same is true for cereals. Is there an association between cereal type (Target: adult, child), and location (Shelf: bottom, middle, top).

```{r}
#| label: cereal-read-data

cereal <- read_csv("CerealFull.csv")
```

Here is the contingency table:

```{r}
#| label: cereal-contingency

tally(Target ~ Shelf, data = cereal)
```


Provide appropriate graphs and summary statistics.

```{r}
#| label: cereal-eda

```






Set up the null and alternative to test for the association between type and location:

$H_0:$  


$H_1:$  


Here is the parametric analysis - do we meet conditions for the parametric analysis?


```{r}
#| label: cereal-parametric

xchisq.test(Target ~ Shelf, data = cereal, correct = FALSE)
```



Set up the nonparametric test and interpret the results to answer the research question.







