---
title: "In-class Activity: Bootstrap Confidence Intervals"
author: "GROUP NUMBER: GROUP MEMBER NAMES"
format: html
embed-resources: true
html-math-method: mathml
execute: 
  warning: false
  echo: true
  error: false
---

```{r}
#| label: setup
#| include: FALSE
#| message: FALSE
library(mosaic)
library(ggformula)
library(readr)
theme_set(theme_light())
```



## Body Temperature

```{r}
temp <- read_csv("BodyTemp.csv")
```


1. Calculate the appropriate summary statistics and graphics

```{r}

```



2. Construct the bootstrap distribution of the sample mean for body temperature

```{r}

```

3. Calculate the 95% and 90% confidence intervals for true mean body temperature. 

```{r}

```


4. Interpret the Confidence Intervals as estimates of the true mean body temperature:

> Insert Answer Here




## Bootstrap for Paired Means

This is really the same as for one-sample, but we will resample the differences instead of the actual values.

A study tested whether wearing wetsuits influences swimming velocity for competative swimmers. Twelve competitive swimmers and triathletes swam 1500m at maximum speed twice each; once wearing a wetsuit and once wearing a regular bathing suit. The order of the trials was randomized. Each time, the maximum velocity in meters/sec of the swimmer was recorded.

```{r}
library(Lock5Data)
data("Wetsuits")

#Calculate the Paired Differences

WetSuits2 <- Wetsuits |> mutate(Paired_Diff = NoWetsuit - Wetsuit) #creates a column of the paired differences

gf_histogram(~Paired_Diff, data = WetSuits2, xlab = "Difference in No Wetsuit vs. Wetsuit Max Velocity", binwidth = 0.01)

df_stats(~Paired_Diff, data = WetSuits2)
```


5. Calculate the 95% Percentile Bootstrap Confidence Interval for the true mean difference between max velocity while not wearing a wetsuit and wearing a wetsuit.


```{r}

```


6. Interpret your confidence interval estimate:

>Insert Answer Here  


7. How would the confidence interval changed if we instead compared wearing a wetsuit versus not wearing a wetsuit?  

>Insert Answer Here 





