---
title: "In-Class Activity 2: Exploratory Data Analysis"
author: "NAME"
format: html
embed-resources: true
html-math-method: mathml
execute: 
  warning: false
  echo: true
  error: false
---

```{r}
#| label: setup

library(readr) #package to be able to read in data
library(________________) #load your graphics package
library(________________) #load your statistics package
```

Before you start.... 

* rename the .qmd with your LastF- at the start of the file name. 
* remember to hit the 'save' button periodically  



## Mole Crab Size

A marine biologist collected a sample of mole crabs at the Salinas River Mouth Beach. 

1. Read in the dataset for the sample of mole crabs. If needed, enter another line of code that will let you inspect the variable names and data. 

```{r}

```


2. The researcher is interested in the size of the mole crabs (measured as the length, in mm, of the carapace). Calculate descriptive statistics to describe the mole crab size. 

```{r}

```


3. Create a visualization for the mole crab size. Be sure to label it completely. 

```{r}

```


4. Describe the shape of the distribution of mole crabe sizes. Provide evidence from your graphic and statistics to support the shape.  

> Insert answer here


5. What might explain the shape of the distribution?  

> Insert answer here  


6. Create a side-by-side boxplot to compare mole crab size by sex.  

Insert code chunk here


7. Calculate summary statistics for mole crab size by sex.  

Insert code chunk here


8. Based on the graphic and summary statistics, is there evidence that the size of the mole crab differs by sex? Justify your answer, including in it how they differ. 

> Insert answer here


### BONUS QUESTION: 

9. Calculate the proportion of mole crabs in the sample that were each sex.

Insert code chunk here


## BONUS QUESTIONS: KING COUNTY   

Let's return to the King County dataset. Recall it has a number of variable measured on newborn infants in King County, WA and their mothers. 

10. Read in the data and inspect it so you can use variable names

```{r}

```


11. A researcher is interested in studying whether a mother that smokes during pregnancy is more likely to have an infant with low birth weight. Calculate the conditional proportions.

```{r}

```


12. Interpret the following values from the contingeny table: 

> 0.12 is the ....  
> 0.9544 is the ....  


13. Calculate the contingency table if you switched your two variables. 

```{r}

```


14. Are the proportions different from your original table? Why? 

> Insert answer


15. Which table answers the reserch question? Justify your answer.  

> Insert answer


16. Create a barplot to visualize the conditional proportions that answer the research question.  

```{r}

```



Still more time? 

Create a research question and produce a graphic not used above to answer it using one of the datasets. 



## Last step

Finish your analysis by rendering your dataset. It should produce a new .html file in your folder. Select it, then select "More -> Export" to download it. That should download to your computer to be able to turn in. 

**Warning! Use good file management procedures!!** 

* Always render right before exporting 
* Don't keep around test files - delete them after you've checked them so you don't accidentally turn in incomplete work
* Download your work to a designated folder for this semester/class



